---
title: "Self_report"
author: "Matt Gehr"
date: "8/30/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readxl)
library(rstatix)
library(devtools)
library(ggbiplot)
```
#Loading in the data 
```{r Loading data}
data<- read_excel(path = "/Users/matthew/Documents/Documents/Professional/Graduate school/UGA/Lab stuff/Perception of videos/ssVEP/Analysis/Self_report/Perception of Videos_UGA.xlsx")
header.true <- function(df) {
 names(df) <- as.character(unlist(df[1,]))
  df[-1,]
}
data<- header.true(data)
presentation_order<- read_excel("/Users/matthew/Documents/Documents/Professional/Graduate school/UGA/Lab stuff/Perception of videos/ssVEP/Analysis/Self_report/Presentation_Order.xlsx")

par_ids<- data$`Enter the Participants ID number`

presentation_order %>%
  filter(Scene_category_37 == 9)
```
#Getting data in order, adding video names, categories, and row means
```{r Segmenting data for graphing}
Flip <- function(x) 10 - x #necessary since we have higher emotions as lower numbers and that is confusing visually 

valence_dat<- data %>%
  .[, grep("How pleasant did the previous scene make you feel?", names(.))] %>%
  sapply(as.numeric) %>%
  Flip() %>%
  `rownames<-` (par_ids) %>%
  t() %>%
  as.data.frame()%>%
  mutate(means = rowMeans(x = .,dims = 1)) %>%
  cbind(presentation_order,.) %>%
  rownames_to_column()

valence_word<- rep("pleasant", nrow(valence_dat))
valence_dat$rowname<- valence_word


arousing_dat<- data %>%
  .[, grep("How aroused did the previous scene make you feel?", names(.))] %>%
  sapply(as.numeric) %>%
  Flip() %>%
  `rownames<-` (par_ids) %>%
  t() %>%
  as.data.frame()%>%
  mutate(means = rowMeans(x = .,dims = 1)) %>%
  cbind(presentation_order,.) %>%
  rownames_to_column()

arousing_word<- rep("aroused", nrow(arousing_dat))
arousing_dat$rowname<- arousing_word


surprised_dat<- data %>%
  .[, grep("How surprised did the previous scene make you feel?", names(.))] %>%
  sapply(as.numeric) %>%
  Flip() %>%
  `rownames<-` (par_ids) %>%
  t() %>%
  as.data.frame()%>%
  mutate(means = rowMeans(x = .,dims = 1)) %>%
  cbind(presentation_order,.) %>%
  rownames_to_column()

surprised_word<- rep("surprised", nrow(surprised_dat))
surprised_dat$rowname<- surprised_word

anger_dat<- data %>%
  .[, grep("How angry did the previous scene make you feel?", names(.))] %>%
  sapply(as.numeric) %>%
  Flip() %>%
  `rownames<-` (par_ids) %>%
  t() %>%
  as.data.frame()%>%
  mutate(means = rowMeans(x = .,dims = 1)) %>%
  cbind(presentation_order,.) %>%
  rownames_to_column()

anger_word<- rep("angry", nrow(anger_dat))
anger_dat$rowname<- anger_word

disgusted_dat<- data %>%
  .[, grep("How disgusted did the previous scene make you feel?", names(.))] %>%
  sapply(as.numeric) %>%
  Flip() %>%
  `rownames<-` (par_ids) %>%
  t() %>%
  as.data.frame()%>%
  mutate(means = rowMeans(x = .,dims = 1)) %>%
  cbind(presentation_order,.)%>%
  rownames_to_column()

disgusted_word<- rep("disgusted", nrow(disgusted_dat))
disgusted_dat$rowname<- disgusted_word

fear_dat<- data %>%
  .[, grep("How fearful did the previous scene make you feel?", names(.))] %>%
  sapply(as.numeric) %>%
  Flip() %>%
  `rownames<-` (par_ids) %>%
  t() %>%
  as.data.frame()%>%
  mutate(means = rowMeans(x = .,dims = 1)) %>%
  cbind(presentation_order,.) %>%
  rownames_to_column()

fear_word<- rep("fearful", nrow(fear_dat))
fear_dat$rowname<- fear_word

action_dat<- data %>%
  .[, grep("How much action was depicted in the scene?", names(.))] %>%
  sapply(as.numeric) %>%
  Flip() %>%
  `rownames<-` (par_ids) %>%
  t() %>%
  as.data.frame()%>%
  mutate(means = rowMeans(x = .,dims = 1)) %>%
  cbind(presentation_order,.)%>%
  rownames_to_column()

action_word<- rep("action", nrow(action_dat))
action_dat$rowname<- action_word

sad_dat<- data %>%
  .[, grep("How sad did the previous scene make you feel?", names(.))] %>%
  sapply(as.numeric) %>%
  Flip() %>%
  `rownames<-` (par_ids) %>%
  t() %>%
  as.data.frame()%>%
  mutate(means = rowMeans(x = .,dims = 1)) %>%
  cbind(presentation_order,.)%>%
  rownames_to_column()

sad_word<- rep("sad", nrow(sad_dat))
sad_dat$rowname<- sad_word

joy_dat<- data %>%
  .[, grep("How joyful did previous the scene make you feel?", names(.))] %>%
  sapply(as.numeric) %>%
  Flip() %>%
  `rownames<-` (par_ids) %>%
  t() %>%
  as.data.frame()%>%
  mutate(means = rowMeans(x = .,dims = 1)) %>%
  cbind(presentation_order,.)%>%
  rownames_to_column()

joy_word<- rep("joyful", nrow(joy_dat))
joy_dat$rowname<- joy_word

```
#Combining data and changing structure of necessary columns 
```{r Combining graphical segmented data}
all_dat<- do.call("rbind", list(action_dat, anger_dat, arousing_dat, disgusted_dat, fear_dat, joy_dat, sad_dat, surprised_dat, valence_dat))

all_avgs<- all_dat %>%
  select(rowname, Video, Category, means) %>%
  `colnames<-` (c("Discrete_emotion", "Video_name", "Vid_category", "response_means")) %>%
  as.data.frame() %>%
  filter(!Video_name == "Practice_Video")

factor_columns<- c("Discrete_emotion", "Video_name", "Vid_category")
all_avgs[factor_columns]<- lapply(all_avgs[factor_columns], factor)
all_avgs$Vid_category<-recode_factor(all_avgs$Vid_category, `999` = "Practice", `1` = "Pleasant", `2` = "Neutral", `3` = "Unpleasant")

all_avgs[rowSums(is.na(all_avgs)) > 0,]
#Check to make sure there are no NAs 
```
#Graphing and averaging by discrete category and dimensional data 
```{r Graphing categorical averages}
graph_avg<-all_avgs %>%
  group_by(Discrete_emotion, Vid_category) %>%
  dplyr::summarize("Category_mean" = mean(response_means),
            "Number of response" = n())

graph_avg %>%
  ggplot(data = ., aes(x = Vid_category, y = Category_mean, fill = Vid_category))+
  geom_bar(position = "dodge", stat = "identity")+
  scale_fill_manual(values = c('blue','grey','red'))+
  labs(title = "Categorical_Discrete_Breakdown")+
  facet_wrap(~Discrete_emotion)


graph_avg_dimensional<- all_avgs %>%
  filter(Discrete_emotion == c("aroused", "pleasant")) %>%
  group_by(Vid_category, Discrete_emotion) %>%
  dplyr::summarize("Category_mean" = mean(response_means),
            "Number of response" = n())

graph_avg_dimensional %>%
  ggplot(data = ., aes(x = Vid_category, y = Category_mean, fill = Vid_category))+
  geom_bar(position = "dodge", stat = "identity")+
  scale_fill_manual(values = c('blue','grey','red'))+
  labs(title = "Categorical_Discrete_Breakdown")+
  facet_wrap(~Discrete_emotion)
```
#Graphing and averaging by scene 
```{r Graphing scene averages}
all_avgs %>%
  group_by(Discrete_emotion, Video_name) %>%
  dplyr::summarize("Category_mean" = mean(response_means))

tiff("/Users/matthew/Documents/Documents/Professional/Graduate school/UGA/Lab stuff/Perception of videos/ssVEP/Analysis/Self_report/Scene_breakdown.tiff", unit = "in", width = 20 , height = 14, res = 300)
all_avgs %>%
  #filter(Discrete_emotion == "fearful",
   #      response_means > 3) %>%
  ggplot(data = ., aes(x = Discrete_emotion, y = response_means, fill = Vid_category))+
  geom_bar(position = "dodge", stat = "identity")+
  scale_fill_manual(values = c('blue','grey','red'))+
  labs(title = "Categorical_Discrete_Breakdown")+
  facet_wrap(~Video_name)+
  theme_classic()+
  theme(axis.text = element_text(size = 10),
        axis.text.x = element_text(size = 15, angle = 45, hjust = 1),
        axis.title = element_text(size = 10, face = "bold"),
        strip.text = element_text(size = 20),
        )
  dev.off()
```
#Significance testing prep: Gets the data in long form with the participant ID, discrete emotion, 
```{r Significance testing prep}
Flip <- function(x) 10 - x #necessary since we have higher emotions as lower numbers and that is confusing visually 

toMatch<- c("How pleasant did the previous scene make you feel?", "How aroused did the previous scene make you feel?", "How disgusted did the previous scene make you feel?", "How fearful did the previous scene make you feel?", "How much action was depicted in the scene?", "How sad did the previous scene make you feel?",  "How joyful did previous the scene make you feel?", "How angry did the previous scene make you feel?", "How surprised did the previous scene make you feel?")

dat_relevant<-data %>%
  .[, grep(paste(toMatch, collapse = "|"), names(.))] %>%
  sapply(as.numeric) %>%
  Flip() %>%
  t()%>%
  as.data.frame() 

presentation_order_long<- presentation_order %>%
  slice(rep(1:n(), each = 9))

dat_long<- data.frame()
  
for (col in 1:ncol(dat_relevant)){
  sliced_col<- dat_relevant[col]
  par_id_tobind<- rep(par_ids[col], each = length(dat_relevant$V1))
  temp1<- cbind(sliced_col, par_id_tobind, presentation_order_long)
  colnames(temp1)<- (c("Response", "Participant_ID", "Video_name", "Video_category"))
  dat_long<- rbind(dat_long, temp1)
}  
  
dat_long<- add_column(dat_long, Discrete_emotion = NA)

dat_long[grep("How.aroused.did.the.previous.scene.make.you.feel?", rownames(dat_long), value = F), "Discrete_emotion"] <- "Aroused"

dat_long[grep("How.pleasant.did.the.previous.scene.make.you.feel?", rownames(dat_long), value = F), "Discrete_emotion"] <- "Pleasant"

dat_long[grep("How.joyful.did.previous.the.scene.make.you.feel?", rownames(dat_long), value = F), "Discrete_emotion"] <- "Joyful"

dat_long[grep("How.surprised.did.the.previous.scene.make.you.feel?", rownames(dat_long), value = F), "Discrete_emotion"] <- "Surprised"

dat_long[grep("How.sad.did.the.previous.scene.make.you.feel?", rownames(dat_long), value = F), "Discrete_emotion"] <- "Sad"

dat_long[grep("How.angry.did.the.previous.scene.make.you.feel?", rownames(dat_long), value = F), "Discrete_emotion"] <- "Angry"

dat_long[grep("How.disgusted.did.the.previous.scene.make.you.feel?", rownames(dat_long), value = F), "Discrete_emotion"] <- "Disgusted"

dat_long[grep("How.fearful.did.the.previous.scene.make.you.feel?", rownames(dat_long), value = F), "Discrete_emotion"] <- "Fearful"

dat_long[grep("How.much.action.was.depicted.in.the.scene?", rownames(dat_long), value = F), "Discrete_emotion"] <- "Action"

cols_to_factor<- c("Participant_ID", "Video_name", "Video_category", "Discrete_emotion")

#dat_long<- dat_long %>%
#  mutate_each(funs(factor(.)), cols_to_factor)  

dat_long <- dat_long %>%
  `colnames<-` (c("Response", "Participant_ID", "Video_name", "Video_Category", "Luminance", "Video_category", "Discrete_emotion"))

dat_long$Video_category<- recode_factor(dat_long$Video_category, `999` = "Practice", `1` = "Pleasant", `2` = "Neutral", `3` = "Unpleasant", `9` = "Removed")

```
#Action ANOVA 
```{r action ANOVA}
action_aov_dat<- dat_long %>%
  filter(Discrete_emotion == "Action",
         !Video_name == "Practice_Video",
         !Video_category == "Removed") %>%
  group_by(Video_category, Participant_ID) %>%
  dplyr::summarize(category_means = mean(Response, na.rm=TRUE)) %>%
  ungroup(.)

action_aov_dat %>%
  group_by(Video_category) %>%
   dplyr::summarize(Means = mean(category_means, na.rm = TRUE))

action_aov_dat %>%
  anova_test(dv = category_means, wid = Participant_ID, within = Video_category)%>%
  get_anova_table() 
pairwise_t_test(data = action_aov_dat,formula = category_means ~ Video_category, paired = FALSE, p.adjust.method = "bonferroni")
```
#Anger ANOVA 
```{r anger ANOVA}
anger_aov_dat<- dat_long %>%
  filter(., Discrete_emotion == "Angry",
         !Video_name == "Practice_Video",
         !Video_category == "Removed") %>%
  group_by(Video_category, Participant_ID) %>%
   dplyr::summarize(category_means = mean(Response)) %>%
  ungroup(.)

anger_aov_dat %>%
  group_by(Video_category) %>%
   dplyr::summarize(Means = mean(category_means, na.rm = TRUE))

anger_aov_dat %>%
  anova_test(dv = category_means, wid = Participant_ID, within = Video_category)%>%
  get_anova_table() 
pairwise_t_test(data = anger_aov_dat,formula = category_means ~ Video_category, paired = FALSE, p.adjust.method = "bonferroni")
```
#Arousal ANOVA 
```{r arousal ANOVA}
arousal_aov_dat<- dat_long %>%
  filter(., Discrete_emotion == "Aroused",
         !Video_name == "Practice_Video",
         !Video_category == "Removed") %>%
  group_by(Video_category, Participant_ID) %>%
   dplyr::summarize("category_means" = mean(Response),
            "Number of response" = n()) %>%
  ungroup(.)

arousal_aov_dat %>%
  group_by(Video_category) %>%
   dplyr::summarize(Means = mean(category_means, na.rm = TRUE))

arousal_aov_dat %>%
  anova_test(dv = category_means, wid = Participant_ID, within = Video_category)%>%
  get_anova_table() 

pairwise_t_test(data = arousal_aov_dat,formula = category_means ~ Video_category, paired = FALSE, p.adjust.method = "bonferroni")
```
#Disgusted ANOVA 
```{r disgusted ANOVA}
disgusted_aov_dat<- dat_long %>%
  filter(., Discrete_emotion == "Disgusted",
         !Video_name == "Practice_Video",
         !Video_category == "Removed") %>%
  group_by(Video_category, Participant_ID) %>%
   dplyr::summarize(category_means = mean(Response)) %>%
  ungroup(.)

disgusted_aov_dat %>%
  group_by(Video_category) %>%
   dplyr::summarize(Means = mean(category_means, na.rm = TRUE))

disgusted_aov_dat %>%
  anova_test(dv = category_means, wid = Participant_ID, within = Video_category)%>%
  get_anova_table() 
pairwise_t_test(data = disgusted_aov_dat,formula = category_means ~ Video_category, paired = FALSE, p.adjust.method = "bonferroni")
```
#Fear ANOVA
```{r fear ANOVA}
fear_aov_dat<- dat_long %>%
  filter(., Discrete_emotion == "Fearful",
         !Video_name == "Practice_Video",
         !Video_category == "Removed") %>%
  group_by(Video_category, Participant_ID) %>%
   dplyr::summarize(category_means = mean(Response)) %>%
  ungroup(.)

fear_aov_dat %>%
  group_by(Video_category) %>%
   dplyr::summarize(Means = mean(category_means, na.rm = TRUE))

fear_aov_dat %>%
  anova_test(dv = category_means, wid = Participant_ID, within = Video_category)%>%
  get_anova_table() 

pairwise_t_test(data = fear_aov_dat,formula = category_means ~ Video_category, paired = FALSE, p.adjust.method = "bonferroni")

```
#Joy ANOVA
```{r Joy ANOVA}
joy_aov_dat<- dat_long %>%
  filter(., Discrete_emotion == "Joyful",
         !Video_name == "Practice_Video",
         !Video_category == "Removed") %>%
  group_by(Video_category, Participant_ID) %>%
   dplyr::summarize(category_means = mean(Response)) %>%
  ungroup(.)

joy_aov_dat %>%
  group_by(Video_category) %>%
   dplyr::summarize(Means = mean(category_means, na.rm = TRUE))

joy_aov_dat %>%
  anova_test(dv = category_means, wid = Participant_ID, within = Video_category)%>%
  get_anova_table() 
pairwise_t_test(data = joy_aov_dat,formula = category_means ~ Video_category, paired = FALSE, p.adjust.method = "bonferroni")

```
#SAD ANOVA
```{r Sad ANOVA}
sad_aov_dat<- dat_long %>%
  filter(., Discrete_emotion == "Sad",
         !Video_name == "Practice_Video",
         !Video_category == "Removed") %>%
  group_by(Video_category, Participant_ID) %>%
   dplyr::summarize(category_means = mean(Response)) %>%
  ungroup(.)

sad_aov_dat %>%
  group_by(Video_category) %>%
   dplyr::summarize(Means = mean(category_means, na.rm = TRUE))

sad_aov_dat %>%
  anova_test(dv = category_means, wid = Participant_ID, within = Video_category)%>%
  get_anova_table() 
pairwise_t_test(data = sad_aov_dat,formula = category_means ~ Video_category, paired = FALSE, p.adjust.method = "bonferroni")

```
#Surprised ANOVA
```{r Surprised ANOVA}
surprised_aov_dat<- dat_long %>%
  filter(., Discrete_emotion == "Surprised",
         !Video_name == "Practice_Video",
         !Video_category == "Removed") %>%
  group_by(Video_category, Participant_ID) %>%
   dplyr::summarize(category_means = mean(Response)) %>%
  ungroup(.)

surprised_aov_dat %>%
  group_by(Video_category) %>%
   dplyr::summarize(Means = mean(category_means, na.rm = TRUE))

surprised_aov_dat %>%
  anova_test(dv = category_means, wid = Participant_ID, within = Video_category)%>%
  get_anova_table() 
pairwise_t_test(data = surprised_aov_dat,formula = category_means ~ Video_category, paired = FALSE, p.adjust.method = "bonferroni")
```
#Valence ANOVA
```{r Valence ANOVA}
valence_aov_dat<- dat_long %>%
  filter(., Discrete_emotion == "Pleasant",
         !Video_name == "Practice_Video",
         !Video_category == "Removed") %>%
  group_by(Video_category, Participant_ID) %>%
   dplyr::summarize(category_means = mean(Response)) %>%
  ungroup(.)

valence_aov_dat %>%
  group_by(Video_category) %>%
   dplyr::summarize(Means = mean(category_means, na.rm = TRUE))

valence_aov_dat %>%
  anova_test(dv = category_means, wid = Participant_ID, within = Video_category)%>%
  get_anova_table() 
pairwise_t_test(data = valence_aov_dat,formula = category_means ~ Video_category, paired = FALSE, p.adjust.method = "bonferroni")
```
#PCA stuff 
```{r PCA organizing data}
example<- mtcars

example.pca<- prcomp(mtcars[])


pca_action<- action_dat %>%
  select(Video, means) %>%
  remove_rownames(.) %>% 
  column_to_rownames(var="Video") %>%
  `colnames<-` (c("Action"))

pca_anger<- anger_dat %>%
  select(Video, means) %>%
  remove_rownames(.) %>% 
  column_to_rownames(var="Video") %>%
  `colnames<-` (c("Angry"))

pca_arousal<- arousing_dat%>%
  select(Video, means) %>%
  remove_rownames(.) %>% 
  column_to_rownames(var="Video") %>%
  `colnames<-` (c("Aroused")) 

pca_disgusted<- disgusted_dat %>%
  select(Video, means) %>%
  remove_rownames(.) %>% 
  column_to_rownames(var="Video") %>%
  `colnames<-` (c("Disgusted"))

pca_fear<- fear_dat %>% 
  select(Video, means) %>%
  remove_rownames(.) %>% 
  column_to_rownames(var="Video") %>%
  `colnames<-` (c("Fearful"))

pca_joy<- joy_dat %>%
  select(Video, means) %>%
  remove_rownames(.) %>% 
  column_to_rownames(var="Video") %>%
  `colnames<-` (c("Joyful"))

pca_sad<- sad_dat %>%
  select(Video, means) %>%
  remove_rownames(.) %>% 
  column_to_rownames(var="Video") %>%
  `colnames<-` (c("Sad"))

pca_surprised<- surprised_dat %>%
  select(Video, means) %>%
  remove_rownames(.) %>% 
  column_to_rownames(var="Video") %>%
  `colnames<-` (c("Surprised"))

pca_valence <- valence_dat %>%
  select(Video, means) %>%
  remove_rownames(.) %>% 
  column_to_rownames(var="Video") %>%
  `colnames<-` (c("Pleasant"))

pca_dat<- do.call("cbind", list(pca_action, pca_anger, pca_arousal, pca_disgusted, pca_fear, pca_joy, pca_sad, pca_surprised, pca_valence))

pca_dat<- pca_dat %>%
  filter(!rownames(.)== "Practice_Video")

pca_dat<- pca_dat %>%
  cbind(., presentation_order$Category[2:46]) %>%
  .[order(presentation_order$Category[2:46]),] %>%
  cbind(.,c(rep("Pleasant", 18), rep("Neutral", 9), rep("Unpleasant", 18)))

pca_graph<-prcomp(pca_dat[,c(1:9)], center = TRUE,scale. = TRUE)

ggbiplot(pca_graph, labels = rownames(pca_dat))
ggbiplot(pca_graph, ellipse = TRUE, choices =c(3,4)) 

```
#Graphing PCA data 
```{r PCA graphing data}
#discrete_mean_graph

ggbiplot(pca_graph, ellipse = TRUE, labels= rownames(pca_dat), groups = pca_dat$`c(rep("Pleasant", 18), rep("Neutral", 9), rep("Unpleasant", 18))`) +
  scale_color_manual(name = "Condition", values = c("Black", "Blue", "Red"))+
  ggtitle("PCA of All Discrete Emotions")+
  theme_minimal()
#A plot of conditions applied to the scenes. Shows that our classification was not too far off maybe a few videos could be adjusted but not bad for the self report 

#ggbiplot(pca_graph, ellipse = TRUE, choices =c(3,4) , labels= rownames(pca_dat), groups = pca_dat$`c(rep("Pleasant", 18), rep("Neutral", 9), rep("Unpleasant", 18))`)+
#  theme_minimal() +
#  ggtitle("PCA 3 & 4")

pca_graph_negative<-prcomp(pca_dat[,c(2,4,5,7)], center = TRUE,scale. = TRUE)

ggbiplot(pca_graph_negative, ellipse = TRUE, labels= rownames(pca_dat), groups = pca_dat$`c(rep("Pleasant", 18), rep("Neutral", 9), rep("Unpleasant", 18))`)+
  scale_color_manual(name = "Condition", values = c("Black", "Blue", "Red"))+
  theme_minimal() +
  ggtitle("PCA Negative Discrete")

pca_graph_arousing<- prcomp(pca_dat[,c(1,3,8)], center = TRUE,scale. = TRUE)

ggbiplot(pca_graph_arousing, ellipse = TRUE, labels= rownames(pca_dat), groups = pca_dat$`c(rep("Pleasant", 18), rep("Neutral", 9), rep("Unpleasant", 18))`)+
  scale_color_manual(name = "Condition", values = c("Black", "Blue", "Red"))+
  theme_minimal() +
  ggtitle("PCA Arousing Discrete")

pca_graph_dimension<- prcomp(pca_dat[,c(3,9)], center = TRUE,scale. = TRUE)

ggbiplot(pca_graph_dimension, ellipse = TRUE, labels= rownames(pca_dat), groups = pca_dat$`c(rep("Pleasant", 18), rep("Neutral", 9), rep("Unpleasant", 18))`)+
  scale_color_manual(name = "Condition", values = c("Black", "Blue", "Red"))+
  theme_minimal() +
  ggtitle("PCA Dimensional(Valence & Arousing)")
```
#Valence and Arousal with each video as the dat. The category was based on the SSVEPVidSetCon file (/Users/matthew/Documents/Documents/Professional/Graduate school/UGA/Lab stuff/Perception of videos/ssVEP/Analysis/EEG/SSVEP log Files/SSVEPVidSetCon.xlsx)
```{r}
arousing_dat_2 <- arousing_dat %>%
  select(means) %>%
  `colnames<-` (c("arousal_means"))

dimensional_emotion_dat <- cbind.data.frame(valence_dat, arousing_dat_2) %>%
  mutate(Scene_category_37 = case_when(
    grepl(pattern = "1", x = Scene_category_37) ~ "Pleasant",
    grepl(pattern = "2", x = Scene_category_37) ~ "Neutral", 
    grepl(pattern = "3", x = Scene_category_37) ~ "Unpleasant",
    grepl(pattern = "9", x = Scene_category_37) ~ "Removed"
  )) %>%
  select(Video, Scene_category_37, arousal_means, means) %>%
#  filter(Scene_category_37 != "To be Removed") %>%
  `colnames<-` (c("Video", "Scene_category_37", "arousal_means", "valence_means"))
dimensional_emotion_dat$Video<- as.factor(dimensional_emotion_dat$Video)
dimensional_emotion_dat$Scene_category_37<- as.factor(dimensional_emotion_dat$Scene_category_37)

ggplot(dimensional_emotion_dat, aes(x = arousal_means , y = valence_means, color = Scene_category_37)) +
  scale_color_manual(values = c("Black", "Blue", "Purple","Red")) + 
    geom_text(aes(label = Video), size = 2, nudge_x = .22)

```

